EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-06-01 05_examples.tex
v1 + few corrections Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

\section{Examples}\label{SecExamples}
In this section we illustrate and benchmark the functionalities and of the \NAME
library and its interfaces as a solver for DMFT through a variety of examples. We also discuss in detail the relevant code parts from different programming languages.

Some tasks -- particularly those associated with the implementation of the DMFT self-consistency -- are inherently independent of \NAME itself, and the impurity solver is agnostic about them. 
Thus, in the implementations using Fortran, Python or other \NAME interfaces to scientific toolboxes we adopt a reverse communication strategy, which requires the user to independently carry out these parts or, equivalently, to exploit existing utilities.

In our examples based on the Fortran APIs we rely on external open-source libraries, such as DMFTtools\footnote{\url{https://github.com/aamaricci/DMFTtools}} (also developed by some of the authors) to perform specific tasks, including the evaluation of the local Green's function, the implementation of the self-consistency, the construction of the tight-binding model or the calculation of the kinetic energy. 
Where appropriate, we include comments that reference these external procedures.
On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself -- see the script \texttt{DMFT.py} \cite{Wallerberger2019CPC}, which handles all these tasks seamlessly.
Similarly, the TRIQS library offers an extensive framework for the manipulation of Green’s functions and related quantities \cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.

\subsection{Hubbard model on the Bethe lattice (Fortran API, {\tt ed\_mode=normal})}\label{SecExamplesBetheDMFT}
The test bed for any DMFT implementation is conventionally considered 
the description of the Mott or metal-to-insulator transition (MIT) 
in a Bethe lattice, i.e., a Cayley tree with coordination number 
$z\to\infty$ \cite{Georges1996RMP,Rozenberg1999PRL,Kotliar1999EPJB,Kotliar2000PRL,Kotliar2002PRL}.
Here, we present a guided implementation of the DMFT 
solution for the Bethe lattice at $T=0$ using \NAME as impurity
solver.
The model under consideration is the Fermi-Hubbard Hamiltonian:
$$
H = -t \sum_{\langle ij\rangle,\s} c^\dagger_{i\s} c_{j\s} + 
    U \sum_i n_{i\up}n_{i\dw},
$$
where $c^\dagger_{i\s}$ ($c_{i\s}$) are the creation (annihilation) 
operators for an electron at site $i$ with spin $\s$, and 
$n_{i\s} = c^\dagger_{i\s} c_{i\s}$ is the corresponding occupation 
operator. The first sum runs over nearest-neighbor pairs
$\langle ij \rangle$.
We consider the system defined on a Bethe lattice with density of states
$\rho(\e)=\frac{2}{\pi D^2}\sqrt{D^2-\e^2}$,
where $D=2t$ is the half-bandwidth.
Within DMFT framework \cite{Georges1996RMP}, this lattice model is mapped onto a quantum impurity problem with an effective electronic bath that must be determined self-consistently.

@@

\subsubsection{Finite temperature (W2Dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTW2D}
To demonstrate the usage of the W2Dynamics interface to \NAME,  here we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using W2Dynamics. 
In order to showcase the capabilities of \NAME to address low-temperature problems, we compare the continuous-time Quantum Monte Carlo (CTQMC) solver using the hybridization expansion method (CT-HYB) included in W2Dynamics against the \NAME solver at finite temperature.

@@

The W2Dynamics configuration file for the solution of the Bethe lattice problem at finite temperature reads: 
\begin{lstlisting}[style=mybash,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
[General]
DOS             = Bethe           # support for the Bethe lattice is built-in
half-bandwidth  = 1               # list of half-bandwidths per orbital
NAt             = 1               # number of impurities
beta            = 100             # inverse temperature
mu              = 1.0             # chemical potential set to achieve half-filling
EPSN            = 0.0             # turns off filling-based chemical potential search
DMFTsteps       = 100             # given no convergence checking, we might want fewer
magnetism       = para            # symmetrize self-energies per spin
FileNamePrefix  = bethe_dmft_U2   # prefix for the output file name
fileold         = bethe_dmft*hdf5 # file to read an initial self-energy from
readold         = 0               # iteration number to read initial self-energy from, 0 turns off
mixing          = 0.5             # mixing, but mixes self-energies and not Weiss fields
mixing_strategy = linear          # linear mixing as in the Fortran example
FTType          = none            # (for CT-HYB): use the NFFT-measured G
solver          = EDIPACK         # use EDIpack as impurity solver, not default CTHYB

@@

In panel (A) we show the behavior of the imaginary part of the impurity Green's function $\Im{G}(i\omega_n)$ which is the direct output for both methods (note that W2Dynamics does not directly have access to the real-axis Green's function when using the CTQMC solver). In panel (B) we show the same comparison for impurity self-energy $\Im{\Sigma}(i\omega_n)$. 
The results obtained from the three calculations are in excellent agreement one with another already for a small number of bath levels ({\tt NBATH=7}) and relatively low QMC statistics ({\tt Nmeas=200000}).

\subsection{Attractive Hubbard model (Python API, {\tt ed\_mode=superc})}\label{SecExamplesAHM}
The second example we present concerns the DMFT description of the 
attractive Hubbard model \cite{Caffarel1994PRL,Toschi2005NJP,Toschi2005PRB} on a two-dimensional square lattice. This 
example has a twofold aim: (i) to demonstrate the support of \NAME 
for ($s$-wave) superconductivity, and (ii) to illustrate the use of 
the library's Python API through a concrete working example.

The 
model Hamiltonian is given by:
$$
H = \sum_{\ka,\s} \epsilon(\ka) c^\dagger_{\ka\s} c_{\ka\s} 
    - U \sum_i n_{i\up} n_{i\dw},
$$
where $U > 0$, $c^\dagger_{i\s}$ 
is the creation operator for an electron at site $i$ with spin $\s$ and $c^\dagger_{\ka\s} = \tfrac{1}{\sqrt{N}} 
\sum_i e^{-i\ka \cdot R_i} c^\dagger_{i\s}$. 
The occupation operator is $n_{i\s} = c^\dagger_{i\s} c_{i\s}$, and 
the energy dispersion relation is $\e(\ka)=-2t[\cos{(k_x a)}+
\cos{(k_y a)}]$, where we set the lattice spacing 
$a=1$  and the choose the energy unit such as $4t=D=1$ for convenience.

@@

The code implementation closely follows the structure of the previous 
example, with some notable adjustments related to the Nambu basis. 
Specifically, the above symmetries allow one to compute only the 
independent components from the first row, significantly reducing 
the computational effort. 
Note that part of the operations required to implement the DMFT cycle are implemented in the Python module {\tt aux\_funx.py}, adapting from {\tt DMFTtools} functions.  
The initial part of the code handles the 
lattice structure and solver initialization, as described below.

@@

    #Perform self-consistency levaragin {\tt aux\_funx.py} procedures:
    Gmats = get_gloc(wm*1j,ed.xmu,HkNambu,Smats,axis="m")
    Weiss = dmft_weiss_field(Gmats,Smats)

@@

The evolution of the order parameter with attraction $U$ is presented in panel (B). The figure  
highlights the crossover from the weak-coupling BCS regime to the 
strong-coupling BEC regime. In the BCS limit, $\phi$ displays the 
characteristic exponential growth with $U$, known to be 
computationally challenging. In the opposite, strong-coupling, limit 
$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$. The comparison with the BCS mean-field result 
(gray line) reveals the effect of local dynamical fluctuations, which  slightly suppress the order parameter, particularly in the intermediate regime. 
To further quantify these dynamical effects, we plot in the inset of the same panel the 
{\it correlation strength} \cite{Amaricci2015PRL,Amaricci2016PRB}
$\Theta=|S(i\omega\to 0)-S(i\omega\to\infty)|/S(i\omega\to\infty)$. 
Large values of $\Theta$ indicate an anomalous self-energy with 
significant dynamical effects, hence a more correlated superconducting state.
Our results show that the DMFT solution significantly departs from the BCS picture in the strongly correlated intermediate-coupling regime, which is known to host the largest critical temperature \cite{Toschi2005NJP,Toschi2005PRB}.
% A different angle further illustrating the impact of dynamical fluctuations, is reported in panel (D). We show the evolution of the double occupancy $d = \langle n_\up n_\dw \rangle$ as a function of $U$ compared to the MF expression $d = 1/4 + \phi^2$. The DMFT 
% results obtained with \NAME show a slight increase in $d$ over the MF prediction in the BCS regime. As $U$ increases and local correlation becomes sizable, the double occupancy drops below 
% the MF result.

@@

One of the features introduced in \NAME is the possibility of treating local phonons in conjunction with the superconductive phase,
i.e. {\tt ed\_mode=superc}. In order to illustrate this property using a simple application, in this example we discuss the normal and
superconductive solution of the pure Holstein model on the Bethe lattice within DMFT.
We stress that  the code
implementation for this specific case is essentially identical to the listings reported in the sections
\ref{SecExamplesBetheDMFT} ({\tt ed\_mode=normal}) and
\ref{SecExamplesAHM} ({\tt ed\_mode=superc}), provided electron-electron interaction is set to zero and phonon parameters are properly configured.

@@

\paragraph{Results.}
In the following we discuss the adiabatic ($\omega_0\to0$) to
anti-adiabatic ($\omega_0\to\infty$) crossover for
the uniform solution of the Holstein model at constant coupling $\lambda=1.0$.
%
In the anti-adiabatic limit, the Holstein interaction takes a
particularly simple form:
\begin{equation}\label{HlikeAttraction}
    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma\left(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}\right) \Big]^2,
\end{equation}
which describes a local Hubbard-like attraction among electrons
(mediated by local phonons).
In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
enters a Bipolaronic Insulating phase for our
choice of the coupling \cite{Capone2006PRB}.

We characterize the model solution by showing the evolution of the
double occupation $\langle n_{\up}n_{\dw}\rangle$ as a function of the
phonon frequency $\omega_0$, see panel (A) of \figu{figEx5}. In this panel we compare
the behavior for the normal  ({\tt ed\_mode=normal}) against the superconductive
solution ({\tt ed\_mode=superc}). Our results capture the whole
crossover from adiabatic to anti-adiabatic regime. In the former
regime, the double occupation takes a similar value for the two
phases. However, approaching the anti-adiabatic regime, the two
solutions reach the limiting values corresponding to the residual
attraction \equ{HlikeAttraction}.   
To better characterize the nature of the superconducting
phase in the Holstein model, we report the evolution of the anomalous order
parameter $\phi$ in the adiabatic to anti-adiabatic crossover, see panel (B) of \figu{figEx5}.
The DMFT results obtained with \NAME show a rapid increase in the
superconducting order parameter as phonon frequency grows
large. Finally, in the anti-adiabatic regime, $\phi$ saturates to a
finite value corresponding to the attractive Hubbard-like interaction
of strength $\lambda/2$.

@@

\subsection{Interacting Bernevig-Hughes-Zhang model (Fortran API, {\tt ed\_mode=nonsu2})}
In this section we focus on the DMFT solution of the interacting
Bernevig-Hughes-Zhang (BHZ).
As shown in Ref. \cite{Amaricci2023PRB}, at moderate
interactions this model admits an excitonic phase in which opposite
orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2020,Varsano2020NN,Blason2020PRB,Amaricci2023PRB,Giuli2023PRB}

We consider a system of two-orbital electrons on a square
lattice interacting through a Hubbard-Kanamori term and describing
a quantum spin Hall insulator \cite{Kane2005PRL,Bernevig2006S,Hasan2010RMP,Hohenadler2011PRL,Amaricci2015PRL,Tang2017NP,Amaricci2023PRB,Paoletti2024PRB}.
We consider a suitable matrix basis in terms of the Dirac
matrices $\Gamma_{a\a}=\sigma_a\otimes \tau_\a$, where $\sigma_a$ and
$\tau_\a$ are Pauli matrices, respectively, in the spin and orbital
pseudo-spin space. The  model Hamiltonian reads
$$
H = \sum_{k}\psi_{k}^\dagger H(k)\psi_{k} + H_{\rm int},
$$
where $\psi_{k}=[c_{1\uparrow k}, c_{2\uparrow k},
c_{1\downarrow k}, c_{2\downarrow k} ]^T$ is the spinor collecting
annihilation operator $c_{a\sigma k}$ destroying an electron at
orbital $a=1,2$ with spin  $\sigma=\up,\dw$ and lattice momentum
$k$. The non-interacting part of the Hamiltonian is:
$$
H(k) = \left[M-2t(\cos{k_x}+\cos{k_y}) \right]\Gamma_{03} +
   \lambda\sin{k_x}\Gamma_{31} -   \lambda\sin{k_y}\Gamma_{02},
$$
where $M$ is the mass term, which plays the role of a crystal
field splitting among the orbitals. The presence of this term breaks
the symmetry in the orbital pseudo-spin channel.
The  interaction reads: 
$$
   H_{\rm int} = (U-J)\frac{\hat{N}(\hat{N}-1)}{2} - J\left( \frac{1}{4}\hat{N}^2 +
   \hat{S_z}^2 - 2 \hat{T_z}^2\right),
 $$
 where $\hat{N}=\tfrac{1}{2}\psi_i^\dagger \Gamma_{00}\psi_i$ is the
total density operator,
$\hat{S_z}=\tfrac{1}{2}\psi_i^\dagger \Gamma_{30}\psi_i$ is the total
spin polarization operator and $\hat{T_z}=\tfrac{1}{2}\psi_i^\dagger
\Gamma_{03}\psi_i$ is the orbital pseudo-spin polarization operator.
This form corresponds to the density-density part of the
Kanamori interaction. We neglect the pair-hopping and spin-flip purely
for numerical reasons \cite{Amaricci2022CPC}. 
%
In the non-interacting regime this model describes a
quantum spin Hall insulator (QSHI) for $M<4t$ and a trivial Band
Insulator (BI) for $M>4t$.
The transition point at $M=4t$ describes the formation of a gapless Dirac state at  $k=[0,0]$.

@@

To complete the overview of \NAME features, we consider another
model of interacting quantum spin-Hall insulator defined on the honeycomb lattice, with two inequivalent sites in the unit cell. Neglecting the Rashba spin-orbit interaction and discarding any ionic character of the unit cell, the noninteracting Kane-Mele Hamiltonian \cite{Kane2005PRLa,Kane2005PRL} can be written in momentum space as
\begin{align*}
    H_\mathrm{KM} = \sum_{{k}} \psi^\dagger_{{k}} H({k}) \psi_{{k}},
\end{align*}
with $\psi_{{k}} = [c_{{k},\mathrm{A},\up},\,c_{{k},\mathrm{B},\up},\,c_{{k},\mathrm{A},\dw},\,c_{{k},\mathrm{B},\dw}]$ and
    \begin{align}
    H({k}) 
    &= x_{{k}}\Gamma_{01} + y_{{k}}\Gamma_{02} + \delta_{{k}}\Gamma_{33}, \label{eq:Hk_kanemele}\\[1mm]
   x_{{k}}&=t\bigl[\cos({k}\cdot{u})+\cos({k}\cdot{v})+1\bigr],\nonumber\\
   y_{{k}}&=t\bigl[\sin({k}\cdot{u})+\sin({k}\cdot{v})\bigr],\nonumber \\
   \delta_{{k}}&=2\lambda_\mathrm{so}\bigl[\sin({k}\cdot{u})-\sin({k}\cdot{v}) - \sin({k}\cdot{u} -{k}\cdot{v})\bigr], \nonumber
\end{align}
where ${u} = (3a/2, \sqrt{3}a/2)$, and ${v} = (3a/2, -\sqrt{3}a/2)$ 
are suitable basis vectors for the honeycomb lattice, $t$ is the
nearest-neighbor hopping amplitude and $\lambda_\mathrm{so}$ is 
the amplitude of a complex next-nearest-neighbor hopping,
with a spin-dependent $\pm\tfrac{\pi}{2}$ chiral phase arising from spin-orbit coupling, which is well-known to open a topological gap at the Fermi level \cite{Kane2005PRLa,Kane2005PRL}.
The spinorial $4\times4$ matrices $\Gamma_{a\ell} = \sigma_a\otimes\tau_\ell$ are 
defined in terms of Pauli matrices $\sigma_a$, $\tau_\ell$ referred, respectively 
to spin and sublattice degrees of freedom.
% , with the convention that 
% $\sigma_0$ and $\tau_0$ are $2\times2$ identity matrices.
To investigate the effects of electron-electron repulsion we consider a local Hubbard term \cite{Hohenadler2013ROPIP,Rachel2018ROPIP}:
\begin{equation}
    H_\mathrm{KMH}  = H_\mathrm{KM} 
    + U\sum_{i}\Biggl[
                        \left(n_{i,\up} - \frac{1}{2}\right)
                        \left(n_{i,\dw} - \frac{1}{2}\right)
                      \Biggr],
    \label{eq:KMHmodel}
\end{equation}
where $n_{i,\sigma}=c^\dagger_{i,\sigma}c_{i,\sigma}$ are the 
local spin-density operators. The interaction is written in an explicitly 
particle-hole symmetric form so that the model is at half-filling for zero
chemical potential.

>>>>

\section{Examples}\label{SecExamples}
In this section we illustrate and benchmark the functionalities and of  \NAME
library and its interfaces as a solver for DMFT through a variety of examples. We also discuss in detail the relevant code parts from different programming languages.

Some tasks -- particularly those associated with the implementation of the DMFT self-consistency -- are inherently independent of \NAME itself, and the impurity solver is agnostic about them. 
Thus, in the implementations using Fortran, Python or other \NAME interfaces to scientific toolboxes, we adopt a reverse communication strategy, which requires the user to independently carry out these parts or, equivalently, to take advantage of existing utilities.

In our examples based on the Fortran APIs, we rely on external open-source libraries, such as DMFTtools\footnote{\url{https://github.com/aamaricci/DMFTtools}} (also developed by some of the authors), to perform specific tasks, including evaluating the local Green’s function, implementing the self-consistency, constructing the tight-binding model, or calculating the kinetic energy.
Where appropriate, we include comments that reference these external procedures.

On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself -- see the script \texttt{DMFT.py} \cite{Wallerberger2019CPC}, which seamlessly handles all these tasks.
Similarly, the TRIQS library offers an comprehensive framework fo manipulating Green’s functions and related quantities \cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.

\subsection{Hubbard model on the Bethe lattice (Fortran API, {\tt ed\_mode=normal})}\label{SecExamplesBetheDMFT}
The description of the Mott transition using the Hubbard model on the Bethe lattice is conventionally regarded as the standard test bed for any DMFT implementation.  \cite{Georges1996RMP,Rozenberg1999PRL,Kotliar1999EPJB,Kotliar2000PRL,Kotliar2002PRL}.

Here, we present a guided implementation of the DMFT 
solution for the Bethe lattice at $T=0$ using \NAME as impurity
solver.
The model under consideration is the Fermi-Hubbard Hamiltonian:
$$
H = -t \sum_{\langle ij\rangle,\s} c^\dagger_{i\s} c_{j\s} + 
    U \sum_i n_{i\up}n_{i\dw},
$$
where $c^\dagger_{i\s}$ ($c_{i\s}$) are the creation (annihilation) 
operators for an electron at site $i$ with spin $\s$, and 
$n_{i\s} = c^\dagger_{i\s} c_{i\s}$ is the corresponding occupation 
operator. The first sum runs over nearest-neighbor pairs
$\langle ij \rangle$.
We consider the system defined on a Bethe lattice with density of states
$\rho(\e)=\frac{2}{\pi D^2}\sqrt{D^2-\e^2}$,
where $D=2t$ is the half-bandwidth.
Within DMFT framework \cite{Georges1996RMP}, this lattice model is mapped onto a quantum impurity problem with an effective electronic bath that must be determined self-consistently.

@@

\subsubsection{Finite temperature (W2Dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTW2D}
To demonstrate how the W2Dynamics interface integrates with  \NAME, we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using W2Dynamics. 
In order to showcase the capabilities of \NAME to address low-temperature problems, we compare the continuous-time Quantum Monte Carlo (CTQMC) solver using the hybridization expansion method (CT-HYB) included in W2Dynamics against the \NAME solver at finite temperature.

@@

The following is the W2Dynamics configuration file used to solve the Bethe lattice problem at finite temperature: 
\begin{lstlisting}[style=mybash,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
[General]
DOS             = Bethe           # support for the Bethe lattice is built-in
half-bandwidth  = 1               # list of half-bandwidths per orbital
NAt             = 1               # number of impurities
beta            = 100             # inverse temperature
mu              = 1.0             # chemical potential set to achieve half-filling
EPSN            = 0.0             # turns off filling-based chemical potential search
DMFTsteps       = 100             # given no convergence checking, we might want fewer
magnetism       = para            # symmetrize self-energies per spin
FileNamePrefix  = bethe_dmft_U2   # prefix for the output file name
fileold         = bethe_dmft*hdf5 # file to read an initial self-energy from
readold         = 0               # iteration number to read initial self-energy from, 0 turns off
mixing          = 0.5             # mixing, but mixes self-energies and not Weiss fields
mixing_strategy = linear          # linear mixing as in the Fortran example
FTType          = none            # (for CT-HYB): use the NFFT-measured G
solver          = EDIPACK         # use EDIpack as impurity solver, not default CTHYB

@@

In panel (A) we show the behavior of the imaginary part of the impurity Green's function $\Im{G}(i\omega_n)$ which is the direct output for both methods (note that W2Dynamics does not directly have access to the real-axis Green's function when using the CTQMC solver). In panel (B) we show the same comparison for impurity self-energy $\Im{\Sigma}(i\omega_n)$. 
The results obtained from the three calculations are in excellent agreement with each other already for a small number of bath levels ({\tt NBATH=7}) and relatively low QMC statistics ({\tt Nmeas=200000} with {\tt NC=10} parallel processes).

\subsection{Attractive Hubbard model (Python API, {\tt ed\_mode=superc})}\label{SecExamplesAHM}
The second example we present concerns the DMFT description of the 
attractive Hubbard model \cite{Caffarel1994PRL,Toschi2005NJP,Toschi2005PRB} on a two-dimensional square lattice. 
This  example two main goals: (i) to demonstrate \NAME's support for $s$-wave superconductivity, and (ii) to showcase the Python API through a concrete example.

The 
model Hamiltonian is given by:
$$
H = \sum_{\ka,\s} \epsilon(\ka) c^\dagger_{\ka\s} c_{\ka\s} 
    - U \sum_i n_{i\up} n_{i\dw},
$$
where $U > 0$, $c^\dagger_{i\s}$ 
is the creation operator for an electron at site $i$ with spin $\s$ and $c^\dagger_{\ka\s} = \tfrac{1}{\sqrt{N}} 
\sum_i e^{-i\ka \cdot R_i} c^\dagger_{i\s}$. 
The occupation operator is $n_{i\s} = c^\dagger_{i\s} c_{i\s}$, and 
the energy dispersion relation is $\e(\ka)=-2t[\cos{(k_x a)}+
\cos{(k_y a)}]$, where we set the lattice spacing 
$a=1$  and the choose the energy unit such that $4t=D=1$ for convenience.

@@

The code implementation closely follows the structure of the previous 
example, with some notable adjustments related to the Nambu basis. 
These symmetries allow computing only the 
independent components in the first row, reducing 
the computational effort. 
Note that part of the operations required to implement the DMFT cycle are implemented in the Python module {\tt aux\_funx.py}, adapting from {\tt DMFTtools} functions.  
The initial part of the code handles the 
lattice structure and solver initialization, as described below.

@@

    #Perform self-consistency levaraging {\tt aux\_funx.py} procedures:
    Gmats = get_gloc(wm*1j,ed.xmu,HkNambu,Smats,axis="m")
    Weiss = dmft_weiss_field(Gmats,Smats)

@@

The evolution of the order parameter with attraction $U$ is presented in panel (B). The figure  
highlights the crossover from the weak-coupling BCS regime to the 
strong-coupling BEC regime. In the BCS limit, $\phi$ displays the 
characteristic exponential growth with $U$, known to be 
computationally challenging. In the opposite, strong-coupling, limit 
$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$. The comparison with the BCS mean-field result 
(gray line) reveals the effect of local dynamical fluctuations, which  slightly suppress the order parameter, particularly in the intermediate regime. 
To further quantify these dynamical effects, we plot in the inset of the same panel the 
{\it correlation strength} \cite{Amaricci2015PRL,Amaricci2016PRB}
$\Theta=|S(i\omega\to 0)-S(i\omega\to\infty)|/S(i\omega\to\infty)$. 
Large values of $\Theta$ indicate an anomalous self-energy with 
significant dynamical effects, hence a more correlated superconducting state.
Our results show that the DMFT solution significantly departs from the BCS picture in the strongly correlated intermediate-coupling, a regime known to host the highest critical temperature \cite{Toschi2005NJP,Toschi2005PRB}.
% A different angle further illustrating the impact of dynamical fluctuations, is reported in panel (D). We show the evolution of the double occupancy $d = \langle n_\up n_\dw \rangle$ as a function of $U$ compared to the MF expression $d = 1/4 + \phi^2$. The DMFT 
% results obtained with \NAME show a slight increase in $d$ over the MF prediction in the BCS regime. As $U$ increases and local correlation becomes sizable, the double occupancy drops below 
% the MF result.

@@

One of the new features introduced in \NAME is the support for local phonons in combination with superconductivity,
i.e. {\tt ed\_mode=superc}. In order to illustrate this property using a simple application, in this example we discuss the normal and
superconductive solution of the pure Holstein model on the Bethe lattice within DMFT.
Note that the code
implementation for this case is essentially identical to the listings in the previous sections
\ref{SecExamplesBetheDMFT} ({\tt ed\_mode=normal}) and
\ref{SecExamplesAHM} ({\tt ed\_mode=superc}), provided electron-electron interaction is set to zero and phonon parameters are properly configured.

@@

\paragraph{Results.}
In the following we discuss the adiabatic ($\omega_0\to0$) to
anti-adiabatic ($\omega_0\to\infty$) crossover for
the uniform solution of the Holstein model at constant coupling $\lambda=1.0$.
%
In the anti-adiabatic limit, the Holstein interaction takes a
particularly simple form:
\begin{equation}\label{HlikeAttraction}
    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma\left(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}\right) \Big]^2,
\end{equation}
which describes a local Hubbard-like attraction among electrons
(mediated by local phonons).
In the  adiabatic limit, $\omega_0 \rightarrow 0$ the system
enters a Bipolaronic Insulating phase for our
choice of the coupling \cite{Capone2006PRB}.

We characterize the model solution by showing the evolution of the
double occupation $\langle n_{\up}n_{\dw}\rangle$ as a function of the
phonon frequency $\omega_0$, see panel (A) of \figu{figEx5}. In this panel we compare
the behavior for the normal phase ({\tt ed\_mode=normal}) and the superconductive
phase ({\tt ed\_mode=superc}). Our results capture the whole
crossover from adiabatic to anti-adiabatic regime. In the former
regime, the double occupation takes a similar value for the two
phases. However, approaching the anti-adiabatic regime, the two
solutions reach the limiting values corresponding to the residual
attraction \equ{HlikeAttraction}.   
To better characterize the nature of the superconducting
phase in the Holstein model, we report the evolution of the anomalous order
parameter $\phi$ in the adiabatic to anti-adiabatic crossover, see panel (B) of \figu{figEx5}.
The DMFT results obtained with \NAME show a rapid increase in the
superconducting order parameter as phonon frequency grows
large. Finally, in the anti-adiabatic regime, $\phi$ saturates to a
finite value corresponding to the attractive Hubbard-like interaction
of strength $\lambda/2$.

@@

\subsection{Interacting Bernevig-Hughes-Zhang model (Fortran API, {\tt ed\_mode=nonsu2})}
In this section, we focus on the DMFT solution of the interacting
Bernevig-Hughes-Zhang (BHZ) model.
As shown in Ref. \cite{Amaricci2023PRB}, this model exhibits an excitonic phase at moderate
interactions in which opposite orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2020,Varsano2020NN,Blason2020PRB,Amaricci2023PRB,Giuli2023PRB}

We consider a system of two-orbital electrons on a square
lattice, interacting via a Hubbard-Kanamori term. This system realizes a quantum spin Hall insulator \cite{Kane2005PRL,Bernevig2006S,Hasan2010RMP,Hohenadler2011PRL,Amaricci2015PRL,Tang2017NP,Amaricci2023PRB,Paoletti2024PRB}.
We consider a suitable matrix basis in terms of the Dirac
matrices $\Gamma_{a\a}=\sigma_a\otimes \tau_\a$, where $\sigma_a$ and
$\tau_\a$ are Pauli matrices, respectively, in the spin and orbital
pseudo-spin space. The  model Hamiltonian reads
$$
H = \sum_{k}\psi_{k}^\dagger H(k)\psi_{k} + H_{\rm int},
$$
where $\psi_{k}=[c_{1\uparrow k}, c_{2\uparrow k},
c_{1\downarrow k}, c_{2\downarrow k} ]^T$ is the spinor collecting
annihilation operator $c_{a\sigma k}$ destroying an electron at
orbital $a=1,2$ with spin  $\sigma=\up,\dw$ and lattice momentum
$k$. The non-interacting part of the Hamiltonian is:
$$
H(k) = \left[M-2t(\cos{k_x}+\cos{k_y}) \right]\Gamma_{03} +
   \lambda\sin{k_x}\Gamma_{31} -   \lambda\sin{k_y}\Gamma_{02},
$$
where $M$ is the mass term, which plays the role of a crystal
field splitting among the orbitals. The presence of this term breaks
the symmetry in the orbital pseudo-spin channel.
The  interaction reads: 
$$
   H_{\rm int} = (U-J)\frac{\hat{N}(\hat{N}-1)}{2} - J\left( \frac{1}{4}\hat{N}^2 +
   \hat{S_z}^2 - 2 \hat{T_z}^2\right),
 $$
 where $\hat{N}=\tfrac{1}{2}\psi_i^\dagger \Gamma_{00}\psi_i$ is the
total density operator,
$\hat{S_z}=\tfrac{1}{2}\psi_i^\dagger \Gamma_{30}\psi_i$ is the total
spin polarization operator and $\hat{T_z}=\tfrac{1}{2}\psi_i^\dagger
\Gamma_{03}\psi_i$ is the orbital pseudo-spin polarization operator.
This form corresponds to the density-density part of the
Kanamori interaction. We neglect the pair-hopping and spin-flip purely
for numerical reasons \cite{Amaricci2022CPC}. 
%
In the non-interacting regime this model describes a
quantum spin Hall insulator (QSHI) for $M<4t$ and a trivial Band
Insulator (BI) for $M>4t$.
The transition point at $M=4t$ describes the formation of a gapless Dirac state at  $k=[0,0]$.

@@

To complete the overview of \NAME's features, we consider an additional interacting quantum spin-Hall insulator model, defined on the honeycomb lattice, with two inequivalent sites in the unit cell. Neglecting the Rashba spin-orbit interaction and discarding any ionic character of the unit cell, the noninteracting Kane-Mele Hamiltonian \cite{Kane2005PRLa,Kane2005PRL} can be written in momentum space as
\begin{align*}
    H_\mathrm{KM} = \sum_{{k}} \psi^\dagger_{{k}} H({k}) \psi_{{k}},
\end{align*}
with $\psi_{{k}} = [c_{{k},\mathrm{A},\up},\,c_{{k},\mathrm{B},\up},\,c_{{k},\mathrm{A},\dw},\,c_{{k},\mathrm{B},\dw}]$ and
    \begin{align}
    H({k}) 
    &= x_{{k}}\Gamma_{01} + y_{{k}}\Gamma_{02} + \delta_{{k}}\Gamma_{33}, \label{eq:Hk_kanemele}\\[1mm]
   x_{{k}}&=t\bigl[\cos({k}\cdot{u})+\cos({k}\cdot{v})+1\bigr],\nonumber\\
   y_{{k}}&=t\bigl[\sin({k}\cdot{u})+\sin({k}\cdot{v})\bigr],\nonumber \\
   \delta_{{k}}&=2\lambda_\mathrm{so}\bigl[\sin({k}\cdot{u})-\sin({k}\cdot{v}) - \sin({k}\cdot{u} -{k}\cdot{v})\bigr], \nonumber
\end{align}
where ${u} = (3a/2, \sqrt{3}a/2)$, and ${v} = (3a/2, -\sqrt{3}a/2)$ 
are suitable basis vectors for the honeycomb lattice, $t$ is the
nearest-neighbor hopping amplitude and $\lambda_\mathrm{so}$ is 
the amplitude of a complex next-nearest-neighbor hopping,
with a spin-dependent $\pm\tfrac{\pi}{2}$ chiral phase arising from spin-orbit coupling, which is well-known to open a topological gap at the Fermi level \cite{Kane2005PRLa,Kane2005PRL}.
The spinorial $4\times4$ matrices $\Gamma_{a\ell} = \sigma_a\otimes\tau_\ell$ are 
defined in terms of Pauli matrices $\sigma_a$, $\tau_\ell$ referred, respectively 
to spin and sublattice degrees of freedom.
% , with the convention that 
% $\sigma_0$ and $\tau_0$ are $2\times2$ identity matrices.
To investigate the effects of electron-electron repulsion we consider a local Hubbard term \cite{Hohenadler2013ROPIP,Rachel2018ROPIP}:
\begin{equation}
    H_\mathrm{KMH}  = H_\mathrm{KM} 
    + U\sum_{i}\Biggl[
                        \left(n_{i,\up} - \frac{1}{2}\right)
                        \left(n_{i,\dw} - \frac{1}{2}\right)
                      \Biggr],
    \label{eq:KMHmodel}
\end{equation}
where $n_{i,\sigma}=c^\dagger_{i,\sigma}c_{i,\sigma}$ are the 
local spin-density operators. The interaction is written in an explicitly 
particle-hole symmetric form so that the model is at half-filling for zero
chemical potential.
